Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-04-29 writeup/gz_hubble_data.tex
Wrote a quick version of abstract and summary; removed almost all nred text.

\title{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
%% Use \author, \affil, plus the \and command to format author and affiliation 
%% information.  If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.
%%
%% The \affil should be used to document primary affiliations and the
%% \altaffil should be used for secondary affiliations, titles, or email.

@@

% Note: 250-word limit
This is the data release paper for GZ:Hubble\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.}. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.

@@

\begin{table*}
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

@@

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the ACS-GC. we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
\end{figure*}

@@

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

@@

We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in \hst{} imaging.

The selection criteria for the different morphological categories is summarised in Table \ref{tbl:morphologies}. The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.

\begin{table*}
\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
\begin{tabular}{lllc}
\hline\hline
Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
\hline
Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
\hline\hline
\end{tabular}
\end{table*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images. The value of \pfeatures{} for each panel is (1) Top row: \pfeatures~= 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: \pfeatures~= 1.00, 0.875, 0.875, 0.625, 0.375. \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images. Galaxies are a random selection of images with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$. The measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot. Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
\label{fig:zeta_examples}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents \pfeaturesz=\pfeaturesrest. Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values. In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [d]: The same data as [b], but highlighting the upper and lower limit regions.}
\label{fig:p_vs_p}
\end{figure*}

In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}. To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}. Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift. In each z,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures. We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

{\note
\begin{itemize}
\item talk about where the \hst{} sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debias them  
\end{itemize}
}

>>>>

\title{Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging}
%% Use \author, \affil, plus the \and command to format author and affiliation 
%% information.  If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.
%%
%% The \affil should be used to document primary affiliations and the
%% \altaffil should be used for secondary affiliations, titles, or email.

@@

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in Galaxy Zoo: Hubble are selected from various \textit{HST} Legacy surveys taken with the Advanced Camera for Surveys, including AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S. Galaxies are included for GZH classifications down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to sources as high as $z\simeq4$. The morphological data includes measurements of bulge vs. disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

\begin{table*}
\center
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

@@

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the ACS-GC. we use that, else 3DHST, else MUSYC. More 98\% of the matched spec-$z$'s are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference in this sample. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

%\begin{figure*}
%\center
%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
%\label{fig:speczs}
%\end{figure*}

@@

@@

\subsection{Interface and decision tree}\label{ssec:interface}

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
\end{figure*}

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

@@

We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.

%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.

%\begin{table*}
%\center
%\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
%\begin{tabular}{lllc}
%\hline\hline
%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
%\hline
%Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
%                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
%                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
%Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
%                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
%                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
%Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
%                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
%                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
%Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
%                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
%                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
%                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
%                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
%Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
%                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%\hline\hline
%\end{tabular}
%\end{table*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images. The measured value of \pfeatures{} from GZH for the images in each panel are (1) Top row: \pfeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \pfeatures~= (1.000, 0.875, 0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images. Galaxies in this plot were randomly selected from a distribution with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$. Measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot. Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
\label{fig:zeta_examples}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents \pfeaturesz=\pfeaturesrest. Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values. In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [d]: The same data as [b], but highlighting the upper and lower limit regions.}
\label{fig:p_vs_p}
\end{figure*}

In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}. Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift. In each $z$,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures. We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Uncorrectable                      & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}
